InteroceptionScale (study 2) - Data Analysis

### 2025-07-01 study2/analysis/2_analysis.qmd
lesgoo

set.seed(42)
```

df <- read.csv("../data/data_participants.csv") |> 
  filter(!is.na(MINT_Awareness_ExAc_35))
```

@@

items <- select(df, starts_with("MINT_"))
names(items) <- str_remove(names(items), "MINT_")

colors <- c(MINT="#00BCD4", MINTi="#00838F", IAS="#F44336", MAIA="#FF9800", MAIAi="#EF6C00", BPQ="#795548")
```

@@

  MINT_Deficit_Urin_1 = "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
  MINT_Deficit_Urin_2 = "I often feel the need to urinate even when my bladder is not full",
  MINT_Deficit_Urin_3 = "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
  MINT_Deficit_CaCo_4 = "Sometimes my breathing becomes erratic or shallow and I often don't know why",
  MINT_Deficit_CaCo_5 = "I often feel like I can't get enough oxygen by breathing normally",
  MINT_Deficit_CaCo_6 = "Sometimes my heart starts racing and I often don't know why",
  MINT_Deficit_CaNo_7 = "I often only notice how I am breathing when it becomes loud",
  MINT_Deficit_CaNo_8 = "I only notice my heart when it is thumping in my chest",
  MINT_Deficit_CaNo_9 = "I often only notice how I am breathing when my breathing becomes shallow or irregular",
  MINT_Deficit_Olfa_10 = "I often check the smell of my armpits",
  MINT_Deficit_Olfa_11 = "I often check the smell of my own breath",
  MINT_Deficit_Olfa_12 = "I often check the smell of my farts",
  MINT_Deficit_Sati_13 = "I don't always feel the need to eat until I am really hungry",
  MINT_Deficit_Sati_14 = "Sometimes I don't realise I was hungry until I ate something",
  MINT_Deficit_Sati_15 = "I don't always feel the need to drink until I am really thirsty",
  # MINT_Awareness_SexA_16 = "I always feel in my body if I am sexually aroused",
  # MINT_Awareness_SexA_17 = "I can always tell that I am sexually aroused from the way I feel inside",
  # MINT_Awareness_SexA_18 = "I always know when I am sexually aroused",
  MINT_Awareness_SexS_19 = "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
  MINT_Awareness_SexS_20 = "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
  MINT_Awareness_SexS_21 = "My genital organs are very sensitive to pleasant stimulations",
  MINT_Awareness_SexO_22 = "In general, I am very sensitive to changes in my genital organs",
  MINT_Awareness_SexO_23 = "I can notice even very subtle changes in the state of my genital organs",
  MINT_Awareness_SexO_24 = "I am always very aware of the state of my genital organs, even when I am calm",
  MINT_Awareness_UrSe_25 = "In general, I am very aware of the sensations that are happening when I am urinating",
  MINT_Awareness_UrSe_26 = "In general, I am very aware of the sensations that are happening when I am defecating",
  MINT_Awareness_UrSe_27 = "I often experience a pleasant sensation when relieving myself when urinating or defecating)",
  MINT_Awareness_RelA_28 = "I always know when I am relaxed",
  MINT_Awareness_RelA_29 = "I always feel in my body if I am relaxed",
  MINT_Awareness_RelA_30 = "My body is always in the same specific state when I am relaxed",
  MINT_Awareness_StaS_31 = "Being relaxed is a very different bodily feeling compared to other states (e.g., feeling anxious, sexually aroused or after exercise)",
  MINT_Awareness_StaS_32 = "Being sexually aroused is a very different bodily feeling compared to other states (e.g., feeling anxious, relaxed, or after physical exercise)",
  MINT_Awareness_StaS_33 = "Being anxious is a very different bodily feeling compared to other states (e.g., feeling sexually aroused, relaxed or after exercise)",
  MINT_Awareness_ExAc_34 = "I can always accurately feel when I am about to burp",
  MINT_Awareness_ExAc_35 = "I can always accurately feel when I am about to fart",
  MINT_Awareness_ExAc_36 = "I can always accurately feel when I am about to sneeze",
  MINT_Sensitivity_Card_37 = "In general, I am very sensitive to changes in my heart rate",
  MINT_Sensitivity_Card_38 = "I can notice even very subtle changes in the way my heart beats",
  MINT_Sensitivity_Card_39 = "I often notice changes in my heart rate",
  MINT_Sensitivity_Resp_40 = "I can notice even very subtle changes in my breathing",
  MINT_Sensitivity_Resp_41 = "I am always very aware of how I am breathing, even when I am calm",
  MINT_Sensitivity_Resp_42 = "In general, I am very sensitive to changes in my breathing",
  # MINT_Sensitivity_Sign_43 = "When something important is happening in my life, I can feel immediately feel changes in my heart rate",
  # MINT_Sensitivity_Sign_44 = "When something important is happening in my life, I can immediately feel changes in my breathing",
  # MINT_Sensitivity_Sign_45 = "When something important is happening in my life, I can feel it in my body",
  MINT_Sensitivity_Gast_46 = "I can notice even very subtle changes in what my stomach is doing",
  MINT_Sensitivity_Gast_47 = "In general, I am very sensitive to what my stomach is doing",
  MINT_Sensitivity_Gast_48 = "I am always very aware of what my stomach is doing, even when I am calm",
  MINT_Sensitivity_Derm_49 = "In general, my skin is very sensitive",
  MINT_Sensitivity_Derm_50 = "My skin is susceptible to itchy fabrics and materials",
  MINT_Sensitivity_Derm_51 = "I can notice even very subtle stimulations to my skin (e.g., very light touches)"
  # MINT_Sensitivity_SexC_52 = "When I am sexually aroused, I often feel changes in the way my heart beats (e.g., faster or stronger)",
  # MINT_Sensitivity_SexC_53 = "When I am sexually aroused, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
  # MINT_Sensitivity_SexC_54 = "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)"

@@

  x <- x |> 
    str_replace("MINT_", ifelse(qname, "MINT - ", "")) |> 
    str_replace("MAIA_", ifelse(qname, "MAIA - ", "")) |> 
    str_replace("_", " (") 
  x <- ifelse(str_detect(x, "\\("), paste0(x, ")"), x)

@@

### Cluster Stability

#### Full

@@

ega1 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "leiden",
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=FALSE,
  iter=500,
  seed=3, ncores = 4)

@@

#### Final

items <- items |> 
  select(-contains("UrSe"))
```

@@

ega2 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "leiden",
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=FALSE,
  iter=500,
  seed=3, ncores = 4)

@@

# EGAnet::dimensionStability(ega)
itemstability <- EGAnet::itemStability(ega2, IS.plot=FALSE)
plot(itemstability)
```

@@

dimensions <- list(
  C08 = "CaCo",       # Cardiorespiratory Confusion
  C01 = "UrIn",       # Urointestinal Inaccuracy
  C02 = "Derm",       # Dermatoception
  C10 = "CaNo",       # Cardiorespiratory Noticing
  C13 = "Sati",       # Satiety Noticing

  C14 = "SexS",       # Sexual Arousal Sensitivity
  C07 = "StaS",       # State Specificity
  C09 = "SexO",       # Sexual Organs Sensitivity
  C03 = "ExAc",       # Expulsion Accuracy
  C06 = "RelA",       # Relaxation Awareness

  C05 = "Resp",       # Respiroception
  C11 = "Card",       # Cardioception
  C12 = "Gast",       # Gastroception
  C04 = "Olfa"       # Olfactory Compensation

  # C04 = "SexA",       # Sexual Arousal Awareness
  # C08 = "UrSe",       # Urointestinal Sensitivity
  # C12 = "Sign",       # Signalling
  # C07 = "SexC"        # Sexual Arousal Changes  
)

higher <- make_loadingtable(t(net.loads(ega2$EGA$higher_order, loading.method="revised")$std))
cluster_order <- names(higher)[!names(higher) %in% c("Item", "Cluster", "Max")]

lower <- make_loadingtable(net.loads(ega2$EGA$lower_order, loading.method="revised")$std) |>
  select(names(higher)) |>
  mutate(Cluster = fct_relevel(Cluster, cluster_order)) |>
  arrange(Cluster, desc(Max))

higher$Item <- paste0("M", higher$Item)
# higher$Label <- c("Interoceptive Deficit", "Interoceptive Awareness", "Interoceptive Sensitivity")
higher$Label <- ""
# higher$ID  <- ""
lower <- mutate(lower, Label = labels[paste0("MINT_", Item)], ID=Item, Item = 1:n())

rbind(higher, select(lower, -ID)) |>
# rbind(higher, lower) |>
  datawizard::data_relocate("Label", after = "Item") |>
  datawizard::data_rename(names(dimensions), dimensions) |>
  select(-Cluster, -Max) |> 
  mutate(`|` = "") |> 
  gt::gt() |>
  gt::tab_row_group(
    label = "Items",
    rows = 1:(nrow(lower) + nrow(higher))
  ) |>
  gt::tab_row_group(
    label = "Metaclusters",
    rows = 1:nrow(higher)
  ) |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("red", "white", "green"),
                 domain = c(-1, 1)) |>
  gt::tab_style(
    style = gt::cell_text(size="small", style="italic"),
    locations = gt::cells_body(columns="Label", rows=c(4:45))
  ) |>
  gt::tab_style(
    style = list(gt::cell_text(weight="bold"),
                 gt::cell_fill(color = "#F5F5F5")),
    locations = list(
      gt::cells_row_groups(groups = "Items"),
      gt::cells_row_groups(groups = "Metaclusters")
    )
  ) |>
  gt::fmt_number(columns=-Item, decimals=2) |>
  gt::tab_header(
    title = gt::md("**Item Loadings**"),
    subtitle = "Node centrality"
  ) 
```

>>>>

set.seed(42)

Sys.setenv(CHROMOTE_CHROME = "C:\\Program Files (x86)\\Microsoft\\Edge\\Application\\msedge.exe")
```

```{r}
#| code-fold: true

df <- read.csv("../data/data_participants.csv") |> 
  rename(MINT_Urin_1 = MINT_Deficit_Urin_1,
         MINT_Urin_2 = MINT_Deficit_Urin_2,
         MINT_Urin_3 = MINT_Deficit_Urin_3,
         MINT_CaCo_1 = MINT_Deficit_CaCo_4,
         MINT_CaCo_2 = MINT_Deficit_CaCo_5,
         MINT_CaCo_3 = MINT_Deficit_CaCo_6,
         MINT_CaNo_1 = MINT_Deficit_CaNo_7,
         MINT_CaNo_2 = MINT_Deficit_CaNo_8,
         MINT_CaNo_3 = MINT_Deficit_CaNo_9,
         MINT_Olfa_1 = MINT_Deficit_Olfa_10,
         MINT_Olfa_2 = MINT_Deficit_Olfa_11,
         MINT_Olfa_3 = MINT_Deficit_Olfa_12,
         MINT_Sati_1 = MINT_Deficit_Sati_13,
         MINT_Sati_2 = MINT_Deficit_Sati_14,
         MINT_Sati_3 = MINT_Deficit_Sati_15,
         MINT_SexS_1 = MINT_Awareness_SexS_19,
         MINT_SexS_2 = MINT_Awareness_SexS_20,
         MINT_SexS_3 = MINT_Awareness_SexS_21,
         MINT_SexO_1 = MINT_Awareness_SexO_22,
         MINT_SexO_2 = MINT_Awareness_SexO_23,
         MINT_SexO_3 = MINT_Awareness_SexO_24,
         MINT_UrSe_1 = MINT_Awareness_UrSe_25,
         MINT_UrSe_2 = MINT_Awareness_UrSe_26,
         MINT_UrSe_3 = MINT_Awareness_UrSe_27,
         MINT_RelA_1 = MINT_Awareness_RelA_28,
         MINT_RelA_2 = MINT_Awareness_RelA_29,
         MINT_RelA_3 = MINT_Awareness_RelA_30,
         MINT_StaS_1 = MINT_Awareness_StaS_31,
         MINT_StaS_2 = MINT_Awareness_StaS_32,
         MINT_StaS_3 = MINT_Awareness_StaS_33,
         MINT_ExAc_1 = MINT_Awareness_ExAc_34,
         MINT_ExAc_2 = MINT_Awareness_ExAc_35,
         MINT_ExAc_3 = MINT_Awareness_ExAc_36,
         MINT_Card_1 = MINT_Sensitivity_Card_37,
         MINT_Card_2 = MINT_Sensitivity_Card_38,
         MINT_Card_3 = MINT_Sensitivity_Card_39,
         MINT_Resp_1 = MINT_Sensitivity_Resp_40,
         MINT_Resp_2 = MINT_Sensitivity_Resp_41,
         MINT_Resp_3 = MINT_Sensitivity_Resp_42,
         MINT_Gast_1 = MINT_Sensitivity_Gast_46,
         MINT_Gast_2 = MINT_Sensitivity_Gast_47,
         MINT_Gast_3 = MINT_Sensitivity_Gast_48,
         MINT_Derm_1 = MINT_Sensitivity_Derm_49,
         MINT_Derm_2 = MINT_Sensitivity_Derm_50,
         MINT_Derm_3 = MINT_Sensitivity_Derm_51)

colors <- c(Mint="#00BCD4", metaMint="#673AB7", miniMint="#26A36C", microMint="#8BC34A", 
            IAS="#F44336", MAIA="#FFAD04",  iMAIA="#FF7811", BPQ="#795548")
```

@@

items <- select(df, starts_with("MINT_"))
names(items) <- str_remove(names(items), "MINT_")
```

@@

  MINT_Urin_1 = "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
  MINT_Urin_2 = "I often feel the need to urinate even when my bladder is not full",
  MINT_Urin_3 = "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
  MINT_CaCo_1 = "Sometimes my breathing becomes erratic or shallow and I often don't know why",
  MINT_CaCo_2 = "I often feel like I can't get enough oxygen by breathing normally",
  MINT_CaCo_3 = "Sometimes my heart starts racing and I often don't know why",
  MINT_CaNo_1 = "I often only notice how I am breathing when it becomes loud",
  MINT_CaNo_2 = "I only notice my heart when it is thumping in my chest",
  MINT_CaNo_3 = "I often only notice how I am breathing when my breathing becomes shallow or irregular",
  MINT_Olfa_1 = "I often check the smell of my armpits",
  MINT_Olfa_2 = "I often check the smell of my own breath",
  MINT_Olfa_3 = "I often check the smell of my farts",
  MINT_Sati_1 = "I don't always feel the need to eat until I am really hungry",
  MINT_Sati_2 = "Sometimes I don't realise I was hungry until I ate something",
  MINT_Sati_3 = "I don't always feel the need to drink until I am really thirsty",
  # MINT_SexA_16 = "I always feel in my body if I am sexually aroused",
  # MINT_SexA_17 = "I can always tell that I am sexually aroused from the way I feel inside",
  # MINT_SexA_18 = "I always know when I am sexually aroused",
  MINT_SexS_1 = "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
  MINT_SexS_2 = "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
  MINT_SexS_3 = "My genital organs are very sensitive to pleasant stimulations",
  MINT_SexO_1 = "In general, I am very sensitive to changes in my genital organs",
  MINT_SexO_2 = "I can notice even very subtle changes in the state of my genital organs",
  MINT_SexO_3 = "I am always very aware of the state of my genital organs, even when I am calm",
  MINT_UrSe_1 = "In general, I am very aware of the sensations that are happening when I am urinating",
  MINT_UrSe_2 = "In general, I am very aware of the sensations that are happening when I am defecating",
  MINT_UrSe_3 = "I often experience a pleasant sensation when relieving myself when urinating or defecating)",
  MINT_RelA_1 = "I always know when I am relaxed",
  MINT_RelA_2 = "I always feel in my body if I am relaxed",
  MINT_RelA_3 = "My body is always in the same specific state when I am relaxed",
  MINT_StaS_1 = "Being relaxed is a very different bodily feeling compared to other states (e.g., feeling anxious, sexually aroused or after exercise)",
  MINT_StaS_2 = "Being sexually aroused is a very different bodily feeling compared to other states (e.g., feeling anxious, relaxed, or after physical exercise)",
  MINT_StaS_3 = "Being anxious is a very different bodily feeling compared to other states (e.g., feeling sexually aroused, relaxed or after exercise)",
  MINT_ExAc_1 = "I can always accurately feel when I am about to burp",
  MINT_ExAc_2 = "I can always accurately feel when I am about to fart",
  MINT_ExAc_3 = "I can always accurately feel when I am about to sneeze",
  MINT_Card_1 = "In general, I am very sensitive to changes in my heart rate",
  MINT_Card_2 = "I can notice even very subtle changes in the way my heart beats",
  MINT_Card_3 = "I often notice changes in my heart rate",
  MINT_Resp_1 = "I can notice even very subtle changes in my breathing",
  MINT_Resp_2 = "I am always very aware of how I am breathing, even when I am calm",
  MINT_Resp_3 = "In general, I am very sensitive to changes in my breathing",
  # MINT_Sign_43 = "When something important is happening in my life, I can feel immediately feel changes in my heart rate",
  # MINT_Sign_44 = "When something important is happening in my life, I can immediately feel changes in my breathing",
  # MINT_Sign_45 = "When something important is happening in my life, I can feel it in my body",
  MINT_Gast_1 = "I can notice even very subtle changes in what my stomach is doing",
  MINT_Gast_2 = "In general, I am very sensitive to what my stomach is doing",
  MINT_Gast_3 = "I am always very aware of what my stomach is doing, even when I am calm",
  MINT_Derm_1 = "In general, my skin is very sensitive",
  MINT_Derm_2 = "My skin is susceptible to itchy fabrics and materials",
  MINT_Derm_3 = "I can notice even very subtle stimulations to my skin (e.g., very light touches)"
  # MINT_SexC_52 = "When I am sexually aroused, I often feel changes in the way my heart beats (e.g., faster or stronger)",
  # MINT_SexC_53 = "When I am sexually aroused, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
  # MINT_SexC_54 = "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)"

@@

  x <- x |> 
    str_replace("MINT_", ifelse(qname, "MINT - ", "")) |> 
    str_replace("MAIA_", ifelse(qname, "MAIA - ", "")) |> 
    str_replace("_", " - ")

@@

### Full

#### EGA

@@

ega1 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "leiden",
  allow.singleton = TRUE,
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=FALSE,
  iter=500,
  seed=3, ncores = 4)

@@

#### Hierarchical Clustering

```{r}
#| fig-width: 12
#| fig-height: 14
#| warning: false

hclust <- pvclust::pvclust(items,
                 method.hclust = "ward.D2",
                 method.dist = "correlation",
                 nboot = 1000, quiet=TRUE, parallel=TRUE)
plot(hclust, hang = -1, cex = 0.5)
pvclust::pvrect(hclust, alpha=0.95, max.only=TRUE)
```

### Item Reduction

::: {.panel-tabset}

```{r}
features <- data.frame(
  SexS = rowMeans(select(df, starts_with("MINT_SexS_")), na.rm = TRUE),
  StaS = rowMeans(select(df, starts_with("MINT_StaS_")), na.rm = TRUE),
  SexO = rowMeans(select(df, starts_with("MINT_SexO_")), na.rm = TRUE),
  ExaC = rowMeans(select(df, starts_with("MINT_ExAc_")), na.rm = TRUE),
  RelA = rowMeans(select(df, starts_with("MINT_RelA_")), na.rm = TRUE),
  UrSe = rowMeans(select(df, starts_with("MINT_UrSe_")), na.rm = TRUE),
  CaCo = rowMeans(select(df, starts_with("MINT_CaCo_")), na.rm = TRUE),
  Urin = rowMeans(select(df, starts_with("MINT_Urin_")), na.rm = TRUE),
  Sati = rowMeans(select(df, starts_with("MINT_Sati_")), na.rm = TRUE),
  Derm = rowMeans(select(df, starts_with("MINT_Derm_")), na.rm = TRUE),
  CaNo = rowMeans(select(df, starts_with("MINT_CaNo_")), na.rm = TRUE),
  Olfa = rowMeans(select(df, starts_with("MINT_Olfa_")), na.rm = TRUE),
  Resp = rowMeans(select(df, starts_with("MINT_Resp_")), na.rm = TRUE),
  Card = rowMeans(select(df, starts_with("MINT_Card_")), na.rm = TRUE),
  Gast = rowMeans(select(df, starts_with("MINT_Gast_")), na.rm = TRUE)
)

features$CardGast = rowMeans(select(features, Card, Gast), na.rm = TRUE)
features$CardResp = rowMeans(select(features, Card, Resp), na.rm = TRUE)
features$CardRespGast = rowMeans(select(features, Card, Resp, Gast), na.rm = TRUE)

rez <- data.frame()
for(outcome_group in c("Interoception", "Alexithymia", "Mood", "Mental", "Physical", "Biofeedback", "Dissociative", "ER", "Primals", "Lifestyle")) {
  if(outcome_group == "Interoception") {
    outcomes <- c("IAS", "BPQ", "MAIA_EmotionalAwareness", 
                  "MAIA_BodyListening", "MAIA_SelfRegulation",
                  "MAIA_AttentionRegulation", "MAIA_Trusting")
  } else if(outcome_group == "Alexithymia") {
    outcomes <- c("TAS_EOT", "TAS_DDF", "TAS_DIF")
  } else if(outcome_group == "Mood") {
    outcomes <- c("LifeSatisfaction", "PHQ4_Anxiety", "PHQ4_Depression", "ERS_Arousal", "ERS_Sensitivity", "ERS_Persistence")
  } else if (outcome_group == "Mental") {
    outcomes <- c("Disorders_Psychiatric_MoodTreatment", "Disorders_Psychiatric_AnxietyTreatment",
                  "Disorders_Psychiatric_Eating", "Disorders_Psychiatric_Addiction",
                  "Disorders_Psychiatric_Borderline", "Disorders_Psychiatric_Autism",
                  "Disorders_Psychiatric_ADHD")
  } else if (outcome_group == "Physical") {
    outcomes <- c("Disorders_Somatic_AfferentSensitivity", "Disorders_Somatic_CentralSensitization_N",
                  "Disorders_Somatic_AutonomicDysfunction", "Disorders_Somatic_ImmuneInflammatory")
  } else if (outcome_group == "Biofeedback") {
    outcomes <- c("Wearables_HeartImportance", "Wearables_StepsImportance", 
                  "Wearables_SleepImportance", "Wearables_CalorieIntakeImportance",
                  "Wearables_WeightImportance")
  } else if (outcome_group == "Dissociative") {
    outcomes <- names(select(df, starts_with("CEFSA_")))
  } else if (outcome_group == "ER") {
    outcomes <- names(select(df, starts_with("CERQ_"))) 
  } else if (outcome_group == "Primals") {
    outcomes <- names(select(df, starts_with("PI_")))
  } else if (outcome_group == "Lifestyle") {
    outcomes <- c("Physical_Active", "BMI")
  }

  out_group <- data.frame()
  for(outcome in outcomes) {

    out <- data.frame()
    for(feature in names(features)) {

      dat <- data.frame(Participant = df$Participant)
      dat[[outcome]] <- df[[outcome]]
      dat[[feature]] <- features[[feature]]
      dat <- dat[!is.na(dat[[outcome]]) & !is.na(dat[[feature]]), ]

      f <- as.formula(paste0(outcome, " ~ ", feature))
      if(length(unique(dat[[outcome]])) > 2) {
        m <- lm(f, data = dat)
      } else {
        m <- glm(f, data = dat, family = "binomial")
      }
      out <- rbind(out, data.frame(
        Group = outcome_group,
        Outcome = outcome,
        Dimension = feature,
        R2 = as.numeric(r2(m))[1]
      ))
    }

    out$R2 <- as.numeric(normalize(out$R2))
    out$Rank <- datawizard::ranktransform(1 - out$R2)
    out_group <- rbind(out_group, out)
  }

  ave <- summarize(out_group, R2 = median(R2), Rank = min(Rank), .by="Dimension") |> 
    mutate(Group = outcome_group, Outcome = outcome_group)

  rez <- rbind(rez, out_group, ave)
}

grandave <- rez |> 
  filter(Group != Outcome) |> 
  summarize(R2 = mean(R2), Rank = min(Rank), .by="Dimension") |> 
  mutate(Group = "Average", Outcome = "Average")
```

#### R2

```{r}
rbind(rez, grandave) |> 
  select(-Group, -Rank) |> 
  pivot_wider(names_from = "Outcome", values_from = "R2") |> 
  mutate(Group = case_when(
    Dimension %in% c("Card", "Resp", "Gast", "CardRespGast", "CardResp", "CardGast") ~ "Visceral", 
    Dimension %in% c("RelA", "SexS", "ExaC", "StaS", "SexO", "UrSe") ~ "sensitivity", 
    Dimension %in% c("CaCo", "Urin", "Derm", "Olfa", "Sati", "CaNo") ~ "Deficit", 
    .default = "Other")) |> 
  select(Group, Dimension, Average, Interoception, Biofeedback, ER, 
         Primals, Alexithymia, Dissociative, Mood, 
         Physical, Mental, Lifestyle) |>
  arrange(Group, desc(Average)) |> 
  # select(-Group) |> 
  gt::gt() |> 
  gt::data_color(
    columns = -c(Dimension, Group),
    palette = c("white", "green"),
    domain = c(0, 1)
  ) |>
  gt::fmt_number() |>
  gt::tab_header(
    title = "Variable Importance",
    subtitle = "Normalized Predictive Power (R2)"
  ) |> 
  gt::tab_row_group(
    label = "Sensitivity",
    rows = Group == "sensitivity"
  )  |> 
  gt::tab_row_group(
    label = "Interoception",
    rows = Group == "Visceral"
  ) |> 
  gt::tab_row_group(
    label = "Deficit",
    rows = Group == "Deficit"
  ) |> 
  gt::cols_hide(Group)
```

#### Rank

```{r}
rbind(rez, grandave) |> 
  select(-Group, -R2) |> 
  pivot_wider(names_from = "Outcome", values_from = "Rank") |> 
  mutate(Group = case_when(
    Dimension %in% c("Card", "Resp", "Gast", "CardRespGast", "CardResp", "CardGast") ~ "Visceral", 
    Dimension %in% c("RelA", "SexS", "ExaC", "StaS", "SexO", "UrSe") ~ "sensitivity", 
    Dimension %in% c("CaCo", "Urin", "Derm", "Olfa", "Sati", "CaNo") ~ "Deficit", 
    .default = "Other")) |> 
  datawizard::data_relocate(select=c("Group", "Dimension", "Average", "Interoception")) |>
  arrange(Group, Average) |> 
  gt::gt() |> 
  # gt::fmt_number(columns = "Average") |>
  gt::data_color(
    columns = -c(Dimension, Group),
    palette = c("green", "white"),
    domain = c(1, 18)
  ) |> 
  gt::opt_interactive(page_size_default=20)
```

#### Clusters

```{r}
hclust2 <- rez |>
  filter(Group != Outcome) |>
  select(-Group, -Rank) |>
  pivot_wider(names_from = "Dimension", values_from = "R2") |>
  select(-Outcome) |>
  pvclust::pvclust(
     method.hclust = "average",
     method.dist = "correlation",
     nboot = 1000, quiet=TRUE, parallel=TRUE)

plot(hclust2, hang = -1, cex = 0.5)
pvclust::pvrect(hclust2, alpha=0.95, max.only=TRUE)
```

### Final

```{r}
#| fig-width: 10
#| fig-height: 8
#| fig-keep: "first"
#| code-fold: false

items <- items |> 
  select(
    -contains("UrSe"), # Unstable item
    -contains("StaS"), # Too vague and overlapping
    -contains("SexO"), # Overalapping with SexS

    -contains("CaNo") # Overlap with CaCo
    # -contains("Olfa"), # Unstable metacluster
    # -contains("Sati")
  )
```

::: {.panel-tabset}

#### EGA

@@

ega2 <- bootEGA(
  items,
  EGA.type = "hierEGA",
  model = "glasso",  # BGGM
  algorithm = "leiden",
  # consensus.method = "lowest_tefi",
  allow.singleton = TRUE,
  type="resampling",
  plot.itemStability=FALSE,
  typicalStructure=TRUE,
  plot.typicalGraph=FALSE,
  iter=500,
  seed=3, ncores = 4)

@@

# EGAnet::dimensionStability(ega)
itemstability <- EGAnet::itemStability(ega2, IS.plot=FALSE)
p_stab <- plot(itemstability)
p_stab
```

@@

dimensions <- list(
  C01 = "SexS",       # Sexual Arousal Sensitivity
  C02 = "Derm",       # Dermal Hypersensitivity
  C03 = "Card",       # Cardioception
  C04 = "Sati",       # Satiety Awareness
  C05 = "Gast",       # Gastroception
  C06 = "Olfa",       # Olfactory Compensation
  C07 = "Resp",       # Respiroception
  C08 = "RelA",       # Relaxation Awareness
  C09 = "Urin",       # Urointestinal Inaccuracy
  C10 = "ExAc",       # Expulsion Accuracy
  C11 = "CaCo"       # Cardiorespiratory Confusion
  # C01 = "C01",
  # C02 = "C02",
  # C03 = "C03",
  # C04 = "C04",
  # C05 = "C05",
  # C06 = "C06",
  # C07 = "C07",
  # C08 = "C08",
  # C09 = "C09",
  # C10 = "C10",
  # C11 = "C11",
  # C12 = "C12"
)

higher <- make_loadingtable(t(net.loads(ega2$EGA$higher_order, loading.method="revised")$std)) |> 
  arrange(Item)
cluster_order <- names(higher)[!names(higher) %in% c("Item", "Cluster", "Max")]

lower <- make_loadingtable(net.loads(ega2$EGA$lower_order, loading.method="revised")$std) |>
  select(names(higher)) |>
  mutate(Cluster = fct_relevel(Cluster, cluster_order)) |>
  arrange(Cluster, desc(Max))
dimensions <- dimensions[names(dimensions) %in% names(lower)]

higher$Item <- paste0("M", higher$Item)
# higher$Label <- c("Interoceptive Deficit", "Interoceptive Awareness", "Interoceptive Sensitivity")
higher$Label <- c("Interoceptive Awareness", "Interoceptive Deficit", "Visceroception")
higher$ID  <- ""

lower <- mutate(lower, Label = labels[paste0("MINT_", Item)], ID=Item, Item = 1:n())

tab1 <- rbind(higher, lower) |>
  select(-ID) |>
  datawizard::data_relocate("Label", after = "Item") |>
  datawizard::data_rename(names(dimensions), dimensions[names(dimensions)]) |>
  select(-Cluster, -Max) |> 
  mutate(`|` = "") |> 
  gt::gt() |>
  gt::tab_row_group(
    label = "Items",
    rows = 1:(nrow(lower) + nrow(higher))
  ) |>
  gt::tab_row_group(
    label = "Metaclusters",
    rows = 1:nrow(higher)
  ) |>
  gt::data_color(columns=-Item,
                 method = "numeric",
                 palette = c("red", "white", "green"),
                 domain = c(-1, 1)) |>
  gt::tab_style(
    style = gt::cell_text(size="small", style="italic"),
    locations = gt::cells_body(columns="Label", rows=c(4:36))
  ) |>
  gt::tab_style(
    style = list(gt::cell_text(weight="bold"),
                 gt::cell_fill(color = "#F5F5F5")),
    locations = list(
      gt::cells_row_groups(groups = "Items"),
      gt::cells_row_groups(groups = "Metaclusters")
    )
  ) |>
  gt::fmt_number(columns=-Item, decimals=2) |>
  gt::tab_header(
    title = gt::md("**Item Loadings**"),
    subtitle = "Node centrality"
  ) |> 
  # Metacluster 1
  gt::tab_style(
    style = gt::cell_fill(color = "#81C784"),
    locations = list(
      gt::cells_body(columns="Item", rows=c(1))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#81C784"),
    locations = list(
      gt::cells_column_labels(columns = 3),
      gt::cells_body(columns="Item", rows=c(4:6))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#AED581"),
    locations = list(
      gt::cells_column_labels(columns = 4),
      gt::cells_body(columns="Item", rows=c(7:9))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#DCE775"),
    locations = list(
      gt::cells_column_labels(columns = 5),
      gt::cells_body(columns="Item", rows=c(10:12))
    )
  ) |> 
  gt::tab_style(
    style = gt::cell_fill(color = "#BA68C8"),
    locations = list(
      gt::cells_body(columns="Item", rows=c(2))
    )
  ) |> 
  gt::tab_style(
    style = gt::cell_fill(color = "#BA68C8"),
    locations = list(
      gt::cells_column_labels(columns = 6),
      gt::cells_body(columns="Item", rows=c(13:15))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#9575CD"),
    locations = list(
      gt::cells_column_labels(columns = 7),
      gt::cells_body(columns="Item", rows=c(16:18))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#7986CB"),
    locations = list(
      gt::cells_column_labels(columns = 8),
      gt::cells_body(columns="Item", rows=c(19:21))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#64B5F6"),
    locations = list(
      gt::cells_column_labels(columns = 9),
      gt::cells_body(columns="Item", rows=c(22:24))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#4DD0E1"),
    locations = list(
      gt::cells_column_labels(columns = 10),
      gt::cells_body(columns="Item", rows=c(25:27))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#FF7811"),
    locations = list(
      gt::cells_body(columns="Item", rows=c(3))
    )
  ) |> 
  gt::tab_style(
    style = gt::cell_fill(color = "#FFB74D"),
    locations = list(
      gt::cells_column_labels(columns = 11),
      gt::cells_body(columns="Item", rows=c(28:30))
    )
  ) |>
  gt::tab_style(
    style = gt::cell_fill(color = "#E57373"),
    locations = list(
      gt::cells_column_labels(columns = 12),
      gt::cells_body(columns="Item", rows=c(31:33))
    )
  ) |> 
  gt::tab_style(
    style = gt::cell_fill(color = "#A1887F"),
    locations = list(
      gt::cells_column_labels(columns = 13),
      gt::cells_body(columns="Item", rows=c(34:36))
    )
  ) 
tab1
```

```{r}
#| eva: false

gt::gtsave(tab1, "figures/table1.png", vwidth=1660, expand=0, quiet=TRUE)
```

#### Hierarchical Clustering

```{r}
#| fig-width: 12
#| fig-height: 14
#| warning: false
